### 2019-09-09 manuscript/manuscript.tex
new abstract

\linenumbers
\begin{abstract}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-1.pdf}

@@

@@

Paragraph about large effect loci.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-2.pdf}

  \caption{gc{{\bf A}}: The convergence correlation, averaged across replicate pairs,
    through time. Each line represents the convergence correlation
    $\mathrm{cor}(\Delta p_{s}, \Delta p_{s})$ from a starting reference
    generation $s$ to a later time $t$, which varies along the x-axis; each
  line corresponds to a row of the temporal convergence correlation matrix
depicted to the right.  \gc{{\bf B}: The convergence covariance between
individual pairs of replicates in the \textcite{Kelly2019-dc} data. {\bf C}:  The convergence covariance between
individual pairs of replicates in \parencite{Castro2019-uk} data, for
the two selection lines  (LS1 and LS2) and the control (Ctrl).}}

%We find that for covariances 2 timepoints apart ($k=2
%\times 10$ generations), the $20\%$ right tail is inflated by a of 1.3 (95\% CI
%[1.29, 1.32]), consistent with linked selection creating positive covariance in
%allele frequency change. Under constant directional selection, we expect these
%positive covariances between increasingly distant timepoints to decay to zero
%as additive genetic variance is exhausted by selection and linkage
%disequilibrium decays. Instead we find that for covariances 4 timepoints apart
%($k=4 \times 10$ generations), the left tail of negative covariances is
%inflated by a factor of 1.19 (95\% CI [1.17, 1.21]).

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/figure-3.pdf}

  \caption{A, B: The distribution of temporal covariances calculated in 100kb
    genomic windows from the \textcite{Barghi2019-qy} study, plotted alongside
    an empirical neutral null distribution created by recalculating the
    windowed covariances on \gc{a 1000 sign permutions of} allele
    frequency changes \gc{within tiles}. The
    \gc{histogram} bin number is 88, chosen by cross validation (Supplementary Materials
    \ref{suppfig:barghi-cross-validation-binsize}). In subfigure A, windowed
    covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are separated by $k=2 \times
    10$ generations and in subfigure B the covariances are separated by $k=4
    \times 10$ generations; each $k$ is an off-diagonal from the variance
    diagonal of the temporal covariance matrix (see cartoon of upper-triangle
    of covariance matrix in subfigures A and B, where the first diagonal is the
    variance, and the dark gray indicates which off-diagonal of the covariance
    matrix is plotted in the histograms). C: The lower and upper tail
    probabilities of the observed windowed covariances, at 20\% and 80\%
    quintiles of the empirical neutral null distribution, for varying time
    between allele frequency changes (i.e. which off-diagonal $k$). The
  confidence intervals are  $95\%$ block-bootstrap confidence interval, and the
light gray dashed line indicates the 20\% tail probability expected under the
neutral null.}

@@

We re-analyzed three published temporal genomic datasets and detected the
genome-wide signature of linked selection acting over tens of generations.
Furthermore, we find the dynamics of temporal autocovariance are consistent
with theory; as linkage disequilibria and additive variation for fitness decay
through time, temporal covariance decays. In reanalyzing one study
\parencite{Barghi2019-qy}, we find that after sixty generations, greater than
20\% of the variation in allele frequency change is directly due to the action
linked selection. Capitalizing on replicated evolve-and-resequence study
designs, we characterized the extent to which convergent selection pressures
lead to parallel changes in allele frequency across replicate populations,
finding that the correlation in allele frequency changes varies from 0.1 (in
the \cite{Barghi2019-qy} study) to 0.36 (in the \cite{Kelly2019-dc} study).

@@

One limitation of our current work here is that none of the studies we
re-analyzed had linkage disequilibria data for the evolved populations. Our
theory of temporal autocovariance tells us that the temporal autocovariances a
neutral site experiences is determined by the product of the expected linkage
disequilibrium and additive fitness variation that persists through the
generations. This leads to a clear prediction: regions of higher linkage
disequilibrium and lower recombination should have greater temporal
autocovariance than regions with lower LD and higher recombination.
Unfortunately, we lack a high-resolution recombination map for \emph{D.
simulans} and while there are LD data for \emph{D. simulans}
\parencite{Signor2018-wg} we did not find a relationship between temporal
covariance and LD.

@@

Finally, in re-analyzing the \textcite{Barghi2019-qy} study, we find evidence
of linked selection dynamics more complex than expected under a model of
directional selection occurring until fitness variation is exhausted. This is
due either to a change in the environment and its consequences for the fitness
of regions in the genome, recombination breaking up selected alleles, or
epistatic interactions between loci. It is important to note that the original
study did not intentionally alter the environment in any way; this signal is
attained without intentionally seeking it out. Discerning which of these is
creating negative temporal autocovariance is a sizable challenge, requiring
sequencing each generation and LD data.

Overall, we hope this will encourage more temporal genomic studies in both
laboratory and natural populations. Understanding the dynamics of linked
selection over short timescales can help us finally unite phenotypic studies of
rapid adaptation of polygenic adaptations with a detectable genomic signature,
to address long-standing questions on linked selection, evolutionary
quantitative genetics, and the overall impact selection has on genetic
variation.

>>>>

\linenumbers

\begin{abstract}

  Natural selection can proceed in natural populations over short timescales,
  as evident from numerous studies demonstrating rapid phenotypic change.
  However, detecting these changes genome-wide is difficult, as rapid
  adaptation often proceeds from standing variation or is the result of
  polygenic selection, both of which leave faint genomic signals
  indistinguishable from a noisy background of genetic drift. As we developed
  in another paper \parencite{Buffalo2019-io}, one promising signal comes from
  the covariance between allele frequency changes observable from temporal
  genomic data, e.g. evolve-and-resequence studies. These temporal covariances
  reflect how the change in neutral allele frequency at one timepoint is
  predictive of the changes at later timepoints when there is heritable fitness
  variation in the population, as neutral alleles become stochastically linked
  with selected loci. Since genetic drift does not lead to temporal covariance,
  we can begin to directly estimate what fraction of the variation in allele
  frequency change through time is drift by linked selection. Here, we
  re-analyze two \emph{Drosophila simulans} evolve-and-resequence studies, and
  one artificial selection experiment in mice, to quantify the effects of
  linked selection over short timescales. Additionally, taking advantage of
  selection on replicated populations, we can directly estimate the covariance
  in allele frequency between replicates due to convergent selection pressure.
  Overall, we find that in the three studies we analyzed, linked selection has
  a remarkable impact on short term allele frequency dynamics that previously
  may have been attributed to genetic drift.

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-1.pdf}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{figures/figure-2.pdf}

  \caption{{\bf A}: The convergence correlation, averaged across replicate
    pairs, through time. Each line represents the convergence correlation
    $\mathrm{cor}(\Delta p_{s}, \Delta p_{s})$ from a starting reference
    generation $s$ to a later time $t$, which varies along the x-axis; each
    line corresponds to a row of the temporal convergence correlation matrix
    depicted to the right.  {\bf B}: The convergence covariance between
    individual pairs of replicates in the \textcite{Kelly2019-dc} data. {\bf
    C}:  The convergence covariance between individual pairs of replicates in
\parencite{Castro2019-uk} data, for the two selection lines  (LS1 and LS2) and
the control (Ctrl).}

\begin{figure}[!htb]
  \centering
  \includegraphics[]{figures/figure-3.pdf}

  \caption{{\bf A}, {\bf B}: The distribution of temporal covariances
    calculated in 100kb genomic windows from the \textcite{Barghi2019-qy}
    study, plotted alongside an empirical neutral null distribution created by
    recalculating the windowed covariances on a 1,000 sign permutations of
    allele frequency changes within tiles. The histogram bin number is 88,
    chosen by cross validation (Supplementary Materials
    \ref{suppfig:barghi-cross-validation-binsize}). In subfigure {\bf A}, windowed
    covariances $\cov(\Delta p_t, \Delta p_{t+k})$ are separated by $k=2 \times
    10$ generations and in subfigure {\bf A} the covariances are separated by $k=4
    \times 10$ generations; each $k$ is an off-diagonal from the variance
    diagonal of the temporal covariance matrix (see cartoon of upper-triangle
    of covariance matrix in subfigures {\bf A} and {\bf B}, where the first diagonal is the
    variance, and the dark gray indicates which off-diagonal of the covariance
    matrix is plotted in the histograms). {\bf C}: The lower and upper tail
    probabilities of the observed windowed covariances, at 20\% and 80\%
    quintiles of the empirical neutral null distribution, for varying time
    between allele frequency changes (i.e. which off-diagonal $k$). The
  confidence intervals are  $95\%$ block-bootstrap confidence interval, and the
light gray dashed line indicates the 20\% tail probability expected under the
neutral null.}

@@

\gc{Paragraph about large effect loci.}
%We find that for covariances 2 timepoints apart ($k=2
%\times 10$ generations), the $20\%$ right tail is inflated by a of 1.3 (95\% CI
%[1.29, 1.32]), consistent with linked selection creating positive covariance in
%allele frequency change. Under constant directional selection, we expect these
%positive covariances between increasingly distant timepoints to decay to zero
%as additive genetic variance is exhausted by selection and linkage
%disequilibrium decays. Instead we find that for covariances 4 timepoints apart
%($k=4 \times 10$ generations), the left tail of negative covariances is
%inflated by a factor of 1.19 (95\% CI [1.17, 1.21]).

@@

We re-analyzed three published temporal genomic datasets and detected the
genome-wide signature of linked selection acting over tens of generations.
Furthermore, we find the dynamics of temporal autocovariance are consistent
with theory; the temporal covariance in allele frequencies decays \vb{as both
  the fitness variation associated with particular haplotypes and the linkage
disequilibria between selected and neutral loci decay through time}. In
reanalyzing one study \parencite{Barghi2019-qy}, we find that after sixty
generations, greater than 20\% of the variation in allele frequency change is
directly due to the action linked selection. Capitalizing on replicated
evolve-and-resequence study designs, we characterized the extent to which
convergent selection pressures lead to parallel changes in allele frequency
across replicate populations, finding correlation in allele frequency
changes varies from 0.1 (in the \cite{Barghi2019-qy} study) to 0.36 (in the
\cite{Kelly2019-dc} study). \graham{Are these just repeat numbers from main
text? If so nix this sentence}

@@

One limitation of our current work here is that none of the studies we
re-analyzed had linkage disequilibria data for the evolved populations. Our
theory of temporal autocovariance tells us that the temporal autocovariances a
neutral site experiences is determined by the product of the expected linkage
disequilibrium and additive fitness variation that persists through the
generations \parencite{Buffalo2019-ion}. This leads to a clear prediction:
regions of higher linkage disequilibrium and lower recombination should have
greater temporal autocovariance than regions with lower LD and higher
recombination. Unfortunately, we lack a high-resolution recombination map for
\emph{D. simulans} and while there are LD data for \emph{D. simulans}
\parencite{Signor2018-wg} we did not find a relationship between temporal
covariance and LD. \graham{Is important point. We'll likely need plots for
supp}

@@

Finally, in re-analyzing the \textcite{Barghi2019-qy} study, we find evidence
of complex linked selection dynamics. This is due either to a change in the
environment and its consequences for the fitness of regions in the genome,
recombination breaking up selected alleles, or epistatic interactions between
loci. It is important to note that the original study did not intentionally
alter the environment in any way; this signal is attained without intentionally
seeking it out. Discerning which of these is creating negative temporal
autocovariance is a sizable challenge, requiring sequencing each generation and
LD data.

Overall, we hope this will encourage more temporal genomic studies in both
laboratory and natural populations. Understanding the dynamics of linked
selection over short timescales will help to unite phenotypic studies of rapid
adaptation of polygenic adaptations with a detectable genomic signature, to
address long-standing questions on linked selection, evolutionary quantitative
genetics, and the overall impact selection has on genetic variation.
